Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-04 doc_v2/doc_v2.Rmd
conclusion added

## Sigatures

@@

## Effect of coarseness

@@

>>>>

## Signatures

@@

## Profiles

@@

## Conclusion

The results suggest that the Nominal type I error $\alpha$ value shows dependence on the size of the window of optimization. For a given window of optimization the actual Type I error is comparable to the nominal level for only a select few validation window sizes and for comparable validation window sizes of 30 and 50 as done here, the actual type I error does not seem to vary as much as it varies with the optimization window sizes .
A Test Fail, i.e. tests in which a particular parameter setting did not return a valid result, happens, when the shift to align two signatures is so large, that the remaining overlap is too small to accommodate  windows for validation, depends on whether known-match or known non-matches has predictive value, with test results from different sources having a much higher chance to fail. On conducting an analysis of all known bullet lands using the adjusted chumbley algorithm, Type II error was identified to be least bad for window of validation 30 and window of optimization 120. In case of unsmoothed raw marks (profiles), Type II error increases with the amount of smoothing and least for LOWESS smoothing coarseness value about 0.25 or 0.3. In an effort to identify the level of adaptiveness of the algorithm, comparisons were made between signatures and profiles. Their comparison with respect to validation window size for a fixed optimization window size suggested that, profiles have a total error (i.e all incorrect classification of known-matches and known non-matches) greater than or equal to the total error of signatures for all sizes of validation window. Profiles also fail more number of times than signatures in a test fail (for different coarseness keeping windows fixed and also for different validation windows keeping coarseness fixed) which lets us conclude that the behaviour of the algorithm for the profiles instead of pre-processed signatures is not better. Finally it should be noted that the current version of the adjusted chumbley algorithm seems to fall short when compared to other machine-learning based methods \citet{aoas}, and some level of modification to the deterministic algorithm needs to be identified and tested that would reduce the number of incorrect classifications.
